\subsection{The Foreground}

The foreground of an LCA study is a collection of nodes that represent points in the inventory model where flows are exchanged.  The foreground is modelled as a weighted directed graph in which there is a 1:1 correspondence between nodes and product flows.

The foreground matrix $A_f$ reports the adjacency and weights of edges in the graph, and thus describes the relationships among these nodes.  These nodes typically represent unit processes, but they can also indicate exchanges across an implicit system boundary that encloses the nodes.  If a column in $A_f$ is empty, then that is an indication that the corresponding product flow is excluded from the foreground.  In order for this flow to be accounted for in the model, it must either be ``terminated'' in the dependency matrix $A_d$, or represented in the corresponding column of $B_f$ as an emission.  Flows whose entire column consists of 0s throughout $A_f$, $A_d$, and $B_f$ are ``cut offs'' that exit the model with zero burdens.


\input{fig_fragments}

Generally, the foreground matrix $A_f$ can represent any process-flow model with a 1:1 correspondence between processes and flows, i.e. any allocated supply-and-use table, but some fundamental designs are common.  Some simple foreground models are shown in Figure~\ref{fig:fragments}.  The first (a) is a sequential model, in which each node requires one foreground input and generates one output. This model is equivalent to a ``gate to gate'' model.  Here the weights $k_i$ indicate the amount of the preceding reference flow that is required by the subsequent node.  Figure~\ref{fig:fragments}(b) shows an additive model, in which the outputs of several foreground nodes are added together, equivalent to a ``mixer'' or a horizontal average.  In this arrangement the weights %represent the relative weights of each input, and
should add up to a unit output of the reference node.

add a cyclic model


\subsubsection{Model fragments and subsystem boundaries}


The nodes that make up the foreground of an LCA study describe an implicit system boundary

Most complex


\section{Preparing and Reviewing Aggregation Results}

